Temporality of the Victorian Hospital Patient Transfer Network

### 2025-09-02 reports/paper.qmd
disc

There are some clear avenues of further investigation from the current study.
One of these is the addition of disease transmission dynamics. We chose to neglect these mechanisms due to the complexity of defining and characterising the manner of transmission within a facility -- and this can have confounding effects on the interpretation of observed results. It is believed that CPE, for example, is transmitted through the environment, with

In the current study, we have used a discrete time stepping scheme in order to allow for some non-Markovian behaviour; it is likely that an agent-based model would be a more "accurate" representation. This would allow for "higher-order" behaviours, such as those observed in [@myall_network_2021], where patient pathways through wards in that case, and hospitals in ours, are dependent on their admission history.
However, agent-based models are an order of magnitude more expensive to simulate, due to increased computational and memory requirements. The number of

>>>>

There are some clear avenues of further investigation from the current study.
One of these is the addition of disease transmission dynamics. We chose to neglect these mechanisms due to the complexity of defining and characterising the manner of transmission within a facility -- and this can have confounding effects on the interpretation of observed results. It is believed that CPE, for example, is transmitted through the environment, but commentary on reservoirs and control strategies in the clinical literature [@kotsanas_down_2013,@de_geyter_sink_2017,@meschiari_five-component_2021] suggests that there is no well agreed-on conceptual model of the mechanisms of transmission.

Another research avenue is comparing the results against an agent-based simulation. In the current study, we have used a discrete time stepping scheme in order to allow for some non-Markovian behaviour while still retaining a reasonable simulation time. This results in the loss of the abililty to "track" individual patients through the system. In order to recover this ability, and impose more complex rules about individual patient pathways, an agent-based simulation would be required. These higher-order pathways have been shown to cause significant difference in ward-to-ward movement within hospital facilities in [@myall_network_2021]; similar results would be expected for transfers between facilities. Of course, allowing this would require an order of magnitude more computational power, memory, and time.
